---
title: "Final Project Proposal"
date: "7/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Group Introduction

This study will be conducted by the following individuals:

 - Nicholas Reinicke (NetID: ndr3)
 - Raymond Ordona (NetID: )
 - Apoorva H Srinivasa(NetID: )
 - Madhukar (NetID: )

## Title

Predicting Alcohol By Volume in Craft Beer

## Dataset

For this project we will be utilizing a dataset that contains information on approximately 75,000 different recipies of craft beer. The raw data was sourced from this link: https://www.kaggle.com/jtrofe/beer-recipes. 

After cleaning the data we're left with the following data structure:

```{r}
beer_data = read.csv("data/recipeData_clean.csv")
str(beer_data)
```

Each of these variables describes a particular property of the beer itself or a method of making the beer. In particular, we're interested in the ABV measure which represents the Alcohol By Volume (%) of the final product. It should be noted that the relationship between ABV, Original Gravity, and Final Gravity is already know to be:

\[
ABV=133.62*(OG-FG)
\]

And so we will be interested in determining if we can predict the ABV while excluding the Final Gravity metric. 





